Instructions for *ACL Proceedings

### 2023-06-30 paper/paper.tex
paper

% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

@@

\section{Introduction}

\section{Background and previous work}

\section{Materials and methods}

\section{Results}

\section{Discussion}

>>>>

% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
%\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

@@

\section{Introduction}
TODO:
\begin{itemize}
  \item how
\end{itemize}
\section{Background and previous work}

\section{Materials and methods}
TODO:
\begin{itemize}
  \item creation of dataset (CLEVR)
        \begin{itemize}
          \item multiple 'real' objects in scene
          \item 3 attributes (color, size, shape) differentiate objects
          \item using 'dale' setup to uniquely identify target object
        \end{itemize}
  \item building a language game using EGG
  \item based on feature extractors ResNet/VGG
  \item
  \item setup of discriminating game of objects in image
  \item message encoder/decoder is auto-encoder
  \item
\end{itemize}

\section{Results}
TODO:
\begin{itemize}
  \item DaleTwo:
        \begin{itemize}
          \item small hidden/embedding dims, small vocab -> high accuracy
          \item high hidden/embedding dims, small vocav -> low accuracy
        \end{itemize}
  \item DaleFive:
        \begin{itemize}
          \item small hidden/embedding dims, small vocab -> low accuracy
          \item small hidden/embedding dims, bigger vocab -> higher accuracy
        \end{itemize}
  \item ... test different hidden/embedding dims
  \item ... test 3/4 objects
\end{itemize}

\section{Discussion}
TODO:
\begin{itemize}
  \item maybe calculation of loss (multiplicating instead of summing loss per token), unlikely, since sequence length short -> shouldn't result in big differences
  \item reducing dims of image better the increasing dims of message, increasing dims is not learnable for models
  \item Vocab:
        \begin{itemize}
          \item vocabulary could describe attributes of target image (non-discriminative) or describe only differences (discriminative)
          \item in second case, two images is a far easier task than five images. Hence, much lower accuracy
        \end{itemize}
\end{itemize}
